Towards automated provenance collection for experimental runs of agent-based models

### 2023-07-20 paper/paper.tex
Changed diagrams and such like for the reviewers

\begin{figure} % wrapfigure is too small to see anything useful
    \includegraphics[width=\textwidth]{img/schema.jpeg} % You should use a PNG at >= 300 dpi; not a lossy format like JPEG. You can export PNGs from PDFs using Preview
\caption{SSREPI Schema} \label{fig:schema} \end{figure}

@@

\begin{figure} % I suggest you put 'dir = LR' in this DOT file -- we can't really read the workflow
\includegraphics[width=\textwidth]{img/workflow.pdf}
\caption{The workflow sub-graph} \label{fig:workflow} \end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{img/subsection-of-provenance.png}
\caption{A small sub-section of the provenance graph} \label{fig:sub-provenance}
\end{figure}

So what use is this provenance metadata? Imagine for the purposes of illustration that
we have found a bug in a script. The entity {\color{red}\ttvar{Applications.application_3831436655}} is an experiment setup script \ttvar{SSS-StopC2-Cluster-create.pl}. We can use the workflow graph to see what else in the workflow might be affected. As might be expected for an experiment setup script, there are serious cascading consequences, which we can visualise in Figure \ref{fig:broken-application}. The Dot language used by Graphviz constitutes a primitive graph
database. Indeed there are programs that can transform Dot files into TinkerPop
GraphSON format \cite{tinkerpop2015graphson,gv2graphson}, two reasonably well known and utilised graphing database formats. To generate Figure
\ref{fig:broken-application}, we used the workflow visualisation Dot file
rather than the relational database.

\begin{figure} \includegraphics[width=\textwidth]{img/broken-application.pdf}
\caption{The workflow sub-graph show the propagation of a broken application (in red) to anything transitively making use of its outputs} \label{fig:broken-application} \end{figure}

>>>>

\begin{figure} % wrapfigure is too small to see anything useful
    \includegraphics[width=\textwidth]{img/schema.png} % You should use a PNG at >= 300 dpi; not a lossy format like JPEG. You can export PNGs from PDFs using Preview
    \caption{The overall SSREPI Schema with the workflow part magnified (will be used later in the paper}
    \label{fig:schema} 
\end{figure}

@@

\begin{figure} % I suggest you put 'dir = LR' in this DOT file -- we can't really read the workflow
\includegraphics[width=\textwidth]{img/workflow.png}
\caption{The workflow sub-graph - showing the part of the graph of interest magnified} \label{fig:workflow} \end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{img/subsection-of-provenance.png}
\caption{A small sub-section of the provenance graph - this is deliberately selected to indicate the complexity of the graph and how hard it is to read.} \label{fig:sub-provenance}
\end{figure}

So what use is this provenance metadata, if as shown in fig. \ref{fig:sub-provenance} it is so difficult to read or visualise? Imagine for the purposes of illustration that
we have found a bug in a script. The entity {\color{red}\ttvar{Applications.application_3831436655}} is an experiment setup script \ttvar{SSS-StopC2-Cluster-create.pl}. We can use the workflow graph to see what else in the workflow might be affected. As might be expected for an experiment setup script, there are serious cascading consequences, which we can visualise in Figure \ref{fig:broken-application}. The Dot language used by Graphviz constitutes a primitive graph
database. Indeed there are programs that can transform Dot files into TinkerPop
GraphSON format \cite{tinkerpop2015graphson,gv2graphson}, two reasonably well known and utilised graphing database formats. To generate Figure
\ref{fig:broken-application}, we used the workflow visualisation Dot file
rather than the relational database. In addition we used the workflow sub-graph because this is probably one of the easier graphs to follow visually.

\begin{figure} 
    \includegraphics[width=\textwidth]{img/broken-application.png}
    \caption{The workflow sub-graph show the propagation of a broken application (in red) in the background. The break-out box shows a magnified detail to show the content of the graph.} 
    \label{fig:broken-application} 
\end{figure}
